XXXXX

### 2014-09-22 paper/paper1.tex
OWL 2 QL

\section{Idea}

@@

@@

\section{Requirements Not Expressible By OWL 2 QL}

>>>>

\section{Ideas}

@@

\tb{should we provide an implementation of RDF Validation with OWL 2 QL in the RDF Validator (purl.org/net/rdfval-demo)?}

@@

\section{OWL 2 QL}

OWL 2 profiles specification: \cite{owl2profiles2008}

\begin{itemize}
  \item OWL 2 QL constructs
	\item Difference between OWL 2 DL and OWL 2 QL
\end{itemize}

\section{RDF Validation Requirements Expressible By OWL 2 QL}

\section{RDF Validation Requirements Not Expressible By OWL 2 QL}

\subsection{class-specific disjoint data properties}

\begin{ex}
(foaf:name xsd:string  | foaf:givenName xsd:string+, foaf:familyName xsd:string)
\end{ex}

\subsection{class-specific disjoint object properties}
